Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-04 prob.tex
prob.tex \section{Proofs} Updating...

\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ is
called an \emph{approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
if 
\[
W_{l}\le\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{d-1}}f\left(\ket{\psi_{i}}\right)\le W_{r}
\]
 for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
of $\mathbb{R}^{d}$.\qed\end{definition}

@@

\begin{lemma}\label{lemma:analogLemma20RichmanBridges1999}If $f$
is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
and $\eta=f\left(\ket{0}\right)$, then the oscillation on any latitude
of the symmetrization of $f$ with respect to $\ket{0}$ is at most
$\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
The exact $n$ could be computed to minimize the oscillation when
the function $f$ is given.\qed\end{lemma}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Let $g$ be
the symmetrization of $f$ with respect to $\ket{0}$, then $\omega_{g}\left(\delta\right)=2\omega_{f}\left(\delta\right)$.
Let $\ket{\psi}$ and $\ket{\psi'}$ be points in the northern hemisphere
with the same latitude~$\theta$. Let $a$ be the difference in longitudes
of $\ket{\psi}$ and $\ket{\psi'}$. Take $n$ steps along east-west
great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
due south of $\ket{\psi}$\footnote{\yutsung{Double check how many step at least from $\ket{\psi'}$
to a point $\ket{\psi_{s}}$.}}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, while, from Lemma \footnote{\yutsung{Analog to Lemma 16 in \cite{RichmanBridges1999}... To be
typed...}},
\[
g\left(\ket{\psi_{s}}\right)\ge g\left(\ket{\psi'}\right)-n\left[2f\left(\ket{0}\right)+4\left(W_{r}-W_{l}\right)\right]=g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)\textrm{ .}
\]
When the difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, the length between $\ket{\psi}$ and
$\ket{\psi_{s}}$ is at most $2-2\cos\left(\frac{a^{2}}{n}\right)$,
and hence 
\[
g\left(\ket{\psi}\right)\ge g\left(\ket{\psi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
\]
for $\frac{\pi^{2}}{n}\le\frac{\pi}{2}\Leftrightarrow2\pi\le n$.\footnote{\yutsung{We are going to verify this proof by set $W_{r}-W_{l}=0$.
Since $f$ is continuous in this case, we could solve $n\ge2\pi$
such that $2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)\le\frac{\delta}{2}$
for any $\delta>0$, and then solve $\eta\ge0$ such that $2n\eta\le\frac{\delta}{2}$.}}
\end{proof}
The following theorem is an analog to Theorem~21 in \cite{RichmanBridges1999}.

\begin{thm}\label{thm:analogTheorem21RichmanBridges1999}~ 
\begin{itemize}
\item Let $f$ be a nonnegative continuous\footnote{\yutsung{We need this ``continuous'' to apply Lemma~19 in \cite{RichmanBridges1999},
and need to rewrite Lemma~19 if we want to take away this ``continuous''...}}approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
\item $\ell\left(\ket{\psi}\right)=\ip{0}{\psi}^{2}$ and $Q\left(\ket{\psi}\right)=W\left(1-\ell\left(\ket{\psi}\right)\right)$,
and 
\item $\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{thm}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Note that $g_{f,\ket{0}}$
is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
and that $W_{l}-\eta\le g_{f,\ket{0}}\left(\ket{\psi}\right)\le W_{r}-\eta$
for all $\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
the oscillation of $g_{f,\ket{0}}$ on latitudes is at most $\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)$.

@@

\begin{cor}\label{thm:analogCorollary22RichmanBridges1999}~
\begin{itemize}
\item Let $f$ be a bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, $m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$,
$\eta=f\left(\ket{0}\right)-m$, 
\item $Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)$,
and 
\item $\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
\begin{proof}
Clearly, $f'=f-m$ is a nonnegative frame function of weight~$\left(W_{l}',W_{r}'\right)=\left(W_{l}-3m,W_{r}-3m\right)$
and $W'=\frac{W_{l}'+W_{r}'}{2}=W-3m$. Then, $\eta=f'\left(\ket{0}\right)$
and $g_{f',\ket{0}}=g_{f,\ket{0}}-2m$. Let $Q'\left(\ket{\psi}\right)=Q\left(\ket{\psi}\right)-2m=W'\left(1-\ip{0}{\psi}^{2}\right)$,
and we have $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|=\left|Q'\left(\ket{\psi}\right)-g_{f',\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
from theorem~\ref{thm:analogTheorem21RichmanBridges1999}.
\end{proof}
Corollary~22 in \cite{RichmanBridges1999} is used to prove theorem~23
which is the final step to prove Gleason's theorem in \cite{RichmanBridges1999}.
Theorem~23 reads as the following.

\begin{thm}\label{thm:analogTheorem23RichmanBridges1999}~
\begin{itemize}
\item Let $f$ be a bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, 
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
$\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
and 
\item $\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le?$.\qed\end{thm}
\begin{proof}
Let $\ket{\bar{2}}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{\bar{0}}$.
Then 
\[
\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{\bar{0}}\right)+f\left(\ket{\bar{2}}\right)\right)\right|\le W_{r}-W_{l}
\]
so
\[
f\left(\ket{\bar{2}}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{\bar{0}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
\]
whence $f\left(\ket{2}\right)\le m+W_{r}-W_{l}$. Let $\left(x,y,z\right)=\left(\ip{\psi}{0},\ip{\psi}{1},\ip{\psi}{2}\right)$
denote the coordinates of a point~$\ket{\psi}$ with respect to the
frame~$\left\{ \ket{i}\right\} _{i=0}^{2}$, then $Q\left(\ket{\psi}\right)=Mx^{2}+\left(W-M-m\right)y^{2}+mz^{2}$.

@@

Let $M'=\max_{\ket{\psi}\in S^{2}}f'\left(\ket{\psi}\right)$, $m'=\min_{\ket{\psi}\in S^{2}}f'\left(\ket{\psi}\right)$.
Note that the weight of $f'$ is $\left(W_{l}',W_{r}'\right)=\left(W_{l}-W,W_{r}-W\right)$
and $W'=\frac{W_{l}'+W_{r}'}{2}=0$. Choose an orthonormal basis~$\left\{ \ket{i'}\right\} _{i=0}^{2}$
such that $f'\left(\ket{0'}\right)=M'$ and $f\left(\ket{2'}\right)\le m'+W_{r}'-W_{l}'=m'+W_{r}-W_{l}$.
In this case, the approximating form is$Q'\left(\ket{\psi}\right)=Mx'^{2}-\left(M+m\right)y'^{2}+mz'^{2}$.
By the previous paragraph, for $t$ on the great circle~$y'=z'$,
we have
\[
\left|f'\left(\ket{\psi}\right)-M'\left(x'^{2}-z'^{2}\right)\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)
\]

Notice that the great circles~$x=\pm y$, $y=\pm z$, and $z=\pm x$
on $S^{2}$ divide the sphere into 24 triangles. The 14 vertices are
\[
\begin{array}{rcl}
\left(\pm\frac{1}{\sqrt{3}},\pm\frac{1}{\sqrt{3}},\pm\frac{1}{\sqrt{3}}\right),\quad\left(\pm1,0,0\right),\quad\left(0,\pm1,0\right),\quad\left(0,0,\pm1\right).\end{array}
\]
All 24 triangles congruent to 
\end{proof}

>>>>

\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ is
called an \emph{approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
if 
\[
W_{l}\le\sideset{_{\mathbb{R}}}{_{i=0}^{d-1}}\sum f\left(\ket{\psi_{i}}\right)\le W_{r}
\]
 for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
of $\mathbb{R}^{d}$.\qed\end{definition}

@@

\begin{lemma}\label{lemma:analogLemma20RichmanBridges1999}If $f$
is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
and $\eta=f\left(\ket{0}\right)$, then the oscillation on any latitude
of the symmetrization of $f$ with respect to $\ket{0}$ is at most
$\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
The exact $n$ could be computed to minimize the oscillation when
the function $f$ is given.\qed\end{lemma}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Let $g$ be
the symmetrization of $f$ with respect to $\ket{0}$, then $\omega_{g}\left(\delta\right)=2\omega_{f}\left(\delta\right)$.
Let $\ket{\psi}$ and $\ket{\psi'}$ be points in the northern hemisphere
with the same latitude~$\theta$. Let $a$ be the difference in longitudes
of $\ket{\psi}$ and $\ket{\psi'}$. Take $n$ steps along east-west
great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
due south of $\ket{\psi}$\footnote{\yutsung{Double check how many step at least from $\ket{\psi'}$
to a point $\ket{\psi_{s}}$.}}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, while, from Lemma \footnote{\yutsung{Analog to Lemma 16 in \cite{RichmanBridges1999}... To be
typed...}},
\[
g\left(\ket{\psi_{s}}\right)\ge g\left(\ket{\psi'}\right)-n\left[2f\left(\ket{0}\right)+4\left(W_{r}-W_{l}\right)\right]=g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)\textrm{ .}
\]
When the difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, the length between $\ket{\psi}$ and
$\ket{\psi_{s}}$ is at most $2-2\cos\left(\frac{a^{2}}{n}\right)$,
and hence 
\[
g\left(\ket{\psi}\right)\ge g\left(\ket{\psi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
\]
for $\frac{\pi^{2}}{n}\le\frac{\pi}{2}\Leftrightarrow2\pi\le n$.\footnote{\yutsung{We are going to verify this proof by set $W_{r}-W_{l}=0$.
Since $f$ is continuous in this case, we could solve $n\ge2\pi$
such that $2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)\le\frac{\delta}{2}$
for any $\delta>0$, and then solve $\eta\ge0$ such that $2n\eta\le\frac{\delta}{2}$.}}
\end{proof}
The following theorem is an analog to Theorem~21 in \cite{RichmanBridges1999}.

\begin{thm}\label{thm:analogTheorem21RichmanBridges1999}~ 
\begin{itemize}
\item Let $f$ be a nonnegative continuous\footnote{\yutsung{We need this ``continuous'' to apply Lemma~19 in \cite{RichmanBridges1999},
and need to rewrite Lemma~19 if we want to take away this ``continuous''...}}approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
\item $\ell\left(\ket{\psi}\right)=\ip{0}{\psi}^{2}$ and $Q\left(\ket{\psi}\right)=W\left(1-\ell\left(\ket{\psi}\right)\right)$,
and 
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{thm}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Note that $g_{f,\ket{0}}$
is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
and that $W_{l}-\eta\le g_{f,\ket{0}}\left(\ket{\psi}\right)\le W_{r}-\eta$
for all $\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
the oscillation of $g_{f,\ket{0}}$ on latitudes is at most $\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)$.

@@

\begin{cor}\label{thm:analogCorollary22RichmanBridges1999}~
\begin{itemize}
\item Let $f$ be a bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, $m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$,
$\eta=f\left(\ket{0}\right)-m$, 
\item $Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)$,
and 
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
\begin{proof}
Clearly, $f'=f-m$ is a nonnegative frame function of weight~$\left(W_{l}',W_{r}'\right)=\left(W_{l}-3m,W_{r}-3m\right)$
and $W'=\frac{W_{l}'+W_{r}'}{2}=W-3m$. Then, $\eta=f'\left(\ket{0}\right)$
and $g_{f',\ket{0}}=g_{f,\ket{0}}-2m$. Let $Q'\left(\ket{\psi}\right)=Q\left(\ket{\psi}\right)-2m=W'\left(1-\ip{0}{\psi}^{2}\right)$,
and we have $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|=\left|Q'\left(\ket{\psi}\right)-g_{f',\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
from theorem~\ref{thm:analogTheorem21RichmanBridges1999}.
\end{proof}
Corollary~22 in \cite{RichmanBridges1999} is used to prove theorem~23
which is the final step to prove Gleason's theorem in \cite{RichmanBridges1999}.
Theorem~23 reads as the following.

\begin{thm}\label{thm:analogTheorem23RichmanBridges1999}~
\begin{itemize}
\item Let $f$ be a bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, 
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
$\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
and 
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$.\qed\end{thm}
\begin{proof}
Let $\ket{\bar{2}}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{\bar{0}}$.
Then 
\[
\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{\bar{0}}\right)+f\left(\ket{\bar{2}}\right)\right)\right|\le W_{r}-W_{l}
\]
so
\[
f\left(\ket{\bar{2}}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{\bar{0}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
\]
whence $f\left(\ket{2}\right)\le m+W_{r}-W_{l}$. Let $\left(x,y,z\right)=\left(\ip{\psi}{0},\ip{\psi}{1},\ip{\psi}{2}\right)$
denote the coordinates of a point~$\ket{\psi}$ with respect to the
frame~$\left\{ \ket{i}\right\} _{i=0}^{2}$, then $Q\left(\ket{\psi}\right)=Mx^{2}+\left(W-M-m\right)y^{2}+mz^{2}$.

@@

Let $M'=\max_{\ket{\psi}\in S^{2}}f'\left(\ket{\psi}\right)$, $m'=\min_{\ket{\psi}\in S^{2}}f'\left(\ket{\psi}\right)$.
Note that the weight of $f'$ is $\left(W_{l}',W_{r}'\right)=\left(W_{l}-W,W_{r}-W\right)$
and $W'=\frac{W_{l}'+W_{r}'}{2}=0$. Choose an orthonormal basis~$\left\{ \ket{i'}\right\} _{i=0}^{2}$
such that $f'\left(\ket{0'}\right)=M'$ and $f\left(\ket{2'}\right)\le m'+W_{r}'-W_{l}'=m'+W_{r}-W_{l}$.
In this case, the approximating form is$Q'\left(\ket{\psi}\right)=Mx'^{2}-\left(M+m\right)y'^{2}+mz'^{2}$.
By the previous paragraph, for $t$ on the great circle~$y'=z'$,
we have
\[
\left|f'\left(\ket{\psi}\right)-M'\left(x'^{2}-z'^{2}\right)\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+3\left(W_{r}-W_{l}\right)\right)
\]

Notice that the great circles~$x=\pm y$, $y=\pm z$, and $z=\pm x$
on $S^{2}$ divide the sphere into 24 triangles. The 14 vertices are
\[
\begin{array}{rcl}
\left(\pm\frac{1}{\sqrt{3}},\pm\frac{1}{\sqrt{3}},\pm\frac{1}{\sqrt{3}}\right),\quad\left(\pm1,0,0\right),\quad\left(0,\pm1,0\right),\quad\left(0,0,\pm1\right).\end{array}
\]
All 24 triangles are congruent to
\[
\begin{array}{rcl}
\left(1,0,0\right),\quad\left(\frac{1}{\sqrt{3}},\frac{1}{\sqrt{3}},\frac{1}{\sqrt{3}}\right),\quad\left(\frac{1}{\sqrt{3}},-\frac{1}{\sqrt{3}},\frac{1}{\sqrt{3}}\right).\end{array}
\]
The maximum distance between two vertices is $\frac{2}{\sqrt{3}}$.
So any great circle through a point in the interior of that triangle
must intersect the boundary at a distance at most $\frac{1}{\sqrt{3}}$
from the point.

In particular, because $\ket{0'}$ is on the great circle~$y'=z'$,
the great circle~$y'=z'$ must intersect the boundary of one of the
previous triangles. Let $\ket{\psi}$ be the intersection, the distance
between $\ket{0'}$ and $\ket{\psi}$ is at most $\frac{1}{\sqrt{3}}$.
That is
\[
\left(1-x'\right)^{2}+2z'^{2}=\left(1-x'\right)^{2}+y'^{2}+z'^{2}\le\frac{1}{3}\textrm{ .}
\]
Also $x'^{2}+2z'^{2}=1$. So $2\left(1-x'\right)\le\frac{1}{3}$ or
$x'\ge\frac{5}{6}$ so $2z'^{2}\le\frac{11}{36}$ whence $x'^{2}-z'^{2}\ge\frac{13}{24}>\frac{1}{2}$.
Now $\left|M'\left(x'^{2}-z'^{2}\right)\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)+\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+3\left(W_{r}-W_{l}\right)\right)$
so 
\begin{eqnarray*}
\left|M'\right| & \le & 3\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)+3\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+3\left(W_{r}-W_{l}\right)\right)\\
 & = & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
\end{eqnarray*}
Same for $m'$, so
\begin{eqnarray*}
\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right| & \le & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
\end{eqnarray*}
\end{proof}
